Bivariate_analysis on different datasets

### 2018-02-12 All_analysis.Rmd
cleaning up and adding ancillary features, and a separate testing doc

```{r BIVAN, echo=F}
#----------------------
rm(list=ls())
graphics.off()
library(copula)
library(VineCopula)
#----------------------
source("OurBiCopSelect.R")
#----------------------
# This function takes a bivariable dataset (matrix or dataframe)
# Output : a plot(optional) and rankings as a dataframe

>>>>

```{r BIVAN, echo=F}
library(copula)
source("OurBiCopSelect.R")

# This function takes a bivariable dataset (matrix or dataframe)
# Output : a plot(optional) and rankings as a dataframe
